INTELLIGENT SYSTEMS

### 2021-04-17 papers/paper_8.tex
finish 8.4.2

\subsubsection{Tracking With Updating}
As already mentioned, the two important aspects of the framework are to update the model and allow self-recovery when it is unable to track the target. In order to guarantee these two operations, a confidence assessment of the monitoring results must be carried out. The set of patches Xi, each of which belongs to each frame ($K = k_1$), is passed to the part of the network that performs the re-verification in order to return the "\emph{Trust Score s}" obtained based on the similarity with the target template . This score indicates the confidence level of the monitoring and can then be used to identify any errors that can be corrected with an update of the taget template. When the s score is less than a $\sigma$ threshold. then a failure has occurred. If a failure occurs, then the number of frames ($K = k_2$) would be increased by 1 and then re-detected, on the patches, which would return a new patch $X'$ with a new score $s'$. If $s'> \sigma$, then this will be the new tracking result ending the recovery process. When this occurs, the target template, calculated with the new formula (\ref{newX}) will be updated and then replaced with the last detected. In \ref{newX}, $m$ represents the matching function, $m(a,b)=f(a)^Tf(b)$, used to obtain the Trust Score. 
\begin{equation}\label{newX}
    X'_i = \argmax_{X_{i,k} \in S_i}m(T,X_{i,k})
\end{equation}

>>>>

\subsubsection{Tracking With Updating}
As already mentioned, the two important aspects of the framework are to 
update the model and allow self-recovery when it is unable to track the target. 
In order to guarantee these two operations, a confidence assessment of the 
monitoring results must be carried out. The set of patches $X_i$ belonging to 
each frame in $(K = k_1)$, is passed to the part of the network that performs 
the re-verification in order to return the "\emph{Trust Score s}" obtained based on 
the similarity with the target template. This score indicates the confidence 
level of the monitoring and can then be used to identify any errors that can 
be corrected with an update of the target template. When the $s$ score is less 
than a $\sigma_1$ threshold, then a failure has occurred. If a failure occurs, then the 
number of frames $K = k_2$ is set lower and then re-detection is performed, 
which would return a new patch $X'_i$, calculated with the formula \ref{newX}, and a 
new score $s'$. If $s'> \sigma_1$, then the new tracking patch will be $X'_i$. In \ref{newX}, $m$ 
represents the matching function, $m(a,b)=f(a)^Tf(b)$, used to obtain 
the Trust Score. If $s$ is greater than $\sigma_2$, then the target template $T$ is updated 
with patches $X_i$.
\begin{equation}\label{newX}
    X'_i = \argmax_{X_{i,k} \in S_i}m(T,X_{i,k})
\end{equation}

\subsection{EXPERIMENTS}
\subsubsection{Network Architecture}
The proposed CNN network is similar to that of AlexNet \cite{0893551108} with five convolutional 
layers of which only the first two are followed by two max pool 
layers. The batch normalization \cite{0893551138} and the ReLu layers are present after 
each convolutional layer except the last.

\subsubsection{Training Details}
To train the model, the videos contained in the ImageNet dataset were used, 
more precisely 90\% of the videos are used as a training set and the remaining 
10\% as a validation set. The training cycles are 240K with mini-batch size 8. 
The target template is set in each random frame of each training video. From 
two other random adjacent frames, the background patches and the search 
region are chosen. In the search region, a candidate patch $Xi$ is labeled 
positive if its overlap with the ground truth bounding box is greater than 
0.7, otherwise it is considered negative. As for the background patches, these 
are selected if they have an overlap with the ground truth in the range 0.1 to 
0.5. The number of frames $k_1$ is set to 10, while $k_2$ is equal to 1 (it 
indicates the re-detection process will take place in sequence on each single 
patch that has caused the tracking to fail), while the $\sigma_1$ and $\sigma_2$ thresholds 
are set accordingly to 1.6 and 2.
